Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2016-01-19 paper/paper_acm.tex
adding ref to formalization

The type of all modal $n$-types, \ie types for which $P$ holds, is
defined as \footnote{Note that we omit the $n$
on $\modal_n$ in $\Type_n^\modal$ to ease the reading.} %$\Type^\modal_p$, so 
\begin{mymath}
\Type_n^\modal \ \defeq \sum_{T : \Type_n} P (T).
\end{mymath}%
%
Since basic type formers (dependent products, products, sigma types)
preserve truncation levels, we can leverage all theorems on modalities
presented in~\cite[Chapter 7.7]{hottbook}.
%
We now summarize the main properties that are used in our
formalization. We do not recall the proofs as they are not specific to
our presentation (also the setting using truncated types provides
minor changes), but they can be found in our Coq formalization.

>>>>

The type of all modal $n$-types, \ie types for which $P$ holds, is
defined as \footnote{Note that we omit the $n$
on $\modal_n$ in $\Type_n^\modal$ to ease the reading.} %$\Type^\modal_p$, so 
\begin{mymath}
\Type_n^\modal \ \defeq \sum_{T : \Type_n} P (T).
\end{mymath}%
%
Since basic type formers (dependent products, products, sigma types)
preserve truncation levels, we can leverage all theorems on modalities
presented in~\cite[Chapter 7.7]{hottbook}.
%
We now summarize the main properties that are used in our
formalization. We do not recall the proofs as they are not specific to
our presentation (also the setting using truncated types provides
minor changes), but they can be found in our Coq formalization (see
Section~\ref{sec:formalization}).
